Hypertension and microbiome

### 2019-06-12 articletwo.Rmd
Full
Renaming

    maaslin <- maaslinwrapper(pseq = pseq.genus.core.pruned,
                                    looped = var.BP,
                                    forced = var.CL.min,
                              taxa = taxa(pseq.genus.core.pruned))

@@

df.genus.systm <- meta(pseq.genus.systm) %>%
    tibble::rownames_to_column("id") %>%
    full_join(., abund.genus.systm, by = "id") %>%
    mutate(Anaerotruncus = scale(asin(sqrt(g_Anaerotruncus))),
           Sutterella = scale(asin(sqrt(g_Sutterella))))

>>>>

    maaslin <- maaslinwrapper(pseq = pseq.genus.core.pruned,
                                    looped = var.BP,
                                    forced = var.CL,
                              taxa = taxa(pseq.genus.core.pruned))

@@

df.genus.systm <- meta(pseq.genus) %>%
    tibble::rownames_to_column("id") %>%
    full_join(., abund.genus.systm, by = "id") %>%
    mutate(Anaerotruncus = scale(asin(sqrt(g_Anaerotruncus))),
           Sutterella = scale(asin(sqrt(g_Sutterella))))
